Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
slowly writing the main proof

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra that assigns
\[
\cliels(\Omega^*_c(U) \otimes \fg)
\]
to each open set $U \subset \RR^n$.
\end{thm}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
:= {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

@@

\begin{prp}\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

\section{}

The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.

\smallskip

@@

\label{L:ClieFacDef} 
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.

\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

@@

A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

\section{Convolution algebras over colored operads}

\def\conv{{\rm Conv}}

\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}

\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}

\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

We have implemented the first step in the proof strategy.
This section is devoted to the remaining steps.
First, we explain steps (2)-(4), which are rather formal.
Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
Finally, we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)
\]
where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
\owen{Calibrate notations!}
It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.

Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
is that we only have to prove the factorization algebra part of the main theorem. 
To do so, we first use the universal property of the centralizer to obtain 
a canonical factorization algebra map 
\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).

\smallskip

We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
assume that the structural (natural) quasi-isomorphism
$$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}

\subsection{Strictification}

\owen{Recall the relevant strictification results.}

\owen{Sketch of where ${\tt f}$ comes from.}
Given a cochain complex $M$, every $\fg$-representation $\rho: \fg \to \End(M)$ determines a cocommutative coderivation $\cliels(\fg) \to M$.
Conversely, such a coderivation determines an $L_\infty$ action of $\fg$ on $M$.
\owen{\dots}
Applying these observations to ${\tt B}_f$ disk-by-disk, we obtain the following.

\begin{lmm}
As ${\tt B}_f$ is a $\Disk_n$-algebra in $\fg$-representations,
there is a map of $\Disk_n$-algebras in cochain complexes ${\tt f}:  {\tt U}_n \fg \to {\tt B}$.
\end{lmm}

\owen{I'm not sure how to prove the following, or even if we need to.}

\begin{prp}
The map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras models the original map~$f$.
\end{prp}

\subsection{The convolution $\Disk_n$-algebra}

\owen{Discussion of convolution fact algs commented out below}
%
%To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
%we can associate its Chevalley-Eilenberg cochain complex defined 
%by 
%\begin{equation}
% \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
%\end{equation}
%with its classical differential. 
%\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
%We have the evaluation map 
%\begin{equation}
% \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
%\end{equation}
%given by applying a function on a given tensor in $Sym(\fg[-1])$.
%
%\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
%that is an object of the $\infty$-category 
%$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
% taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
%\end{dfn}
%\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
%Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
%the convolution structure is given by the following composition
%\begin{multline}
% \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
% D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
% \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
% \stackrel{\mu_\sigma^B}\longrightarrow B.
%\end{multline}
%where $\Delta$ is the cocommutative comultiplication.
%In plain formula,
%for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
%\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
%\begin{equation}
% \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
%\end{equation}
%where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
%Note that here, we are using the usual Koszul sign  convention. 
%
%\begin{lmm}
% $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
%\end{lmm}

\owen{Describe it.}

\subsection{Construction of the universal pairing in factorization algebras}\label{SS:constuctionthetaf}

@@

\smallskip

First note that compactly supported form embeds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.

\smallskip

Second, the augmentation of $B$ makes $B(-)$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
$\clies\big(\fg\otimes \Omega (-), B(-) \big)$ as well as follows. 
We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B(-)$. This gives the canonical element element 
 $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
 of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
 The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
 \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
 $B(-)$. We therefore obtain a canonical splitting of factorization algebras 
 \begin{equation}\label{eq:splittingbyaugm}
   \clies\big(\fg\otimes \Omega^*(-), B(-)\big)  \, \cong \, k(-) \oplus \overline{ \clies(\fg\otimes \Omega^*(-), B(-)) )}
 \end{equation}
given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
a natural grading on it.

\smallskip

@@

\smallskip

We extend this construction  to any 
 open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
 More precisely, 
  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
of its connected components. Using, the natural isomorphisms of complexes 
\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
 (natural) decomposition 
\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
 \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
 \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
 \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
\end{multline}
and we can therefore define 
\begin{multline}\label{eq:defineevf}
 \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
 \\ \stackrel{\simeq}\longrightarrow  
\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
 \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
 \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
 \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
\end{multline}
where $\mu_B$ is the canonical structure map of the factorization algebra $B(-)$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
and~\eqref{eq:defevforconnected}.
\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
things to do (like completion) for non-finitely dimensional Lie algebras}
\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B(-)$, simply by defining it onto the prefact alg obtained by tensoring 
out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B(-))$ in that case. Not sure which way is easier to define/mention}

>>>>

\owen{Recall any relevant strictification results.}

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is the tensor product of the unit map $1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

@@

\begin{prp}
\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

We have implemented the first step in the proof strategy.
This section is devoted to the remaining steps.
First, we explain steps (2)-(4), which are rather formal.
Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
Finally, we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\]
where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
\owen{Calibrate notations!}
It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.

\owen{Comment on notations:}
As we work in the setting of factorization algebras on $\RR^n$, 
we will use bold font to indicate such factorization models for $E_n$ algebra statements.
For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
and we use $\bf{f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.

Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
is that we only have to prove the factorization algebra part of the main theorem. 
To do so, we first use the universal property of the centralizer to obtain 
a canonical factorization algebra map 
\[\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\]
where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).

\subsection{Standard manipulations with $L_\infty$ algebras and their modules}

To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
we can associate its Chevalley-Eilenberg cochain complex defined 
by 
\begin{equation}
 \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
\end{equation}
with its classical differential. 
\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
We have the evaluation map 
\begin{equation}
 \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
\end{equation}
given by applying a function on a given tensor in $Sym(\fg[-1])$.

\subsection{Defining the convolution factorization algebra}

The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), \bU_n \fh(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $\bU_n \fh(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), \bU_n \fh(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B$.

@@

\label{L:ClieFacDef} 
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ a (resp. locally constant) factorization algebra.

\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c, \bU_n \fh \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $\bU_n \fh$} 
and $\clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

@@

A special but very interesting case is of course when $\bU_n \fh$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c) \longrightarrow  \cliels( \fh \otimes \Omega^*_c) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

\owen{Add a remark on convolution}
%
%\def\conv{{\rm Conv}}
%
%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
%
%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}
%
%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

\subsection{Construction of the universal pairing in factorization algebras}
\label{SS:constuctionthetaf}

@@

First note that compactly supported form embeds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.

Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
 $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
 of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
 The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
 \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
 $B$. We therefore obtain a canonical splitting of factorization algebras 
 \begin{equation}\label{eq:splittingbyaugm}
   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
 \end{equation}
given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
a natural grading on it.

@@

We extend this construction  to any 
 open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
 More precisely, 
  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
of its connected components. Using, the natural isomorphisms of complexes 
\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
 (natural) decomposition 
\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
 \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
 \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
 \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
\end{multline}
and we can therefore define 
\begin{multline}\label{eq:defineevf}
 \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
 \\ \stackrel{\simeq}\longrightarrow  
\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
 \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
 \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
 \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
\end{multline}
where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
and~\eqref{eq:defevforconnected}.
\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
things to do (like completion) for non-finitely dimensional Lie algebras}
\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}

\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
 \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
\end{equation}
where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
\begin{multline*}
{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
\end{multline*}
We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
\emph{with support $\coprod\limits_{j\in J} U_j$}.   
Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
\end{rmk}
In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
have the following formula generalizing the one for connected open  subsets:
\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
X_j\Big)\right) \end{equation}
where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
is the  structure map of $B$.

\begin{lmm}\label{L:pairingCE}
 The pairing morphism $\ev_f$ defined by formula~\eqref{eq:defineevf} extends to a factorization algebra morphism
 \[\ev_f:  \cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big) 
 \longrightarrow B.\]
\end{lmm}
\begin{proof}

\end{proof}
We write, $1$ for the factorization algebra map defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras.

\begin{lmm}\label{L:ComTriangCent} The triangle 
 $$ \xymatrix{
& \clies ( \fg\otimes \Omega^* , B) \otimes \cliels(\fg\otimes \Omega^*_c   )
\ar[dr]^{\ev_f} & \\
\cliels(\fg\otimes \Omega^*_c ) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B.}
 $$
is a commutative triangle of factorization algebras maps.
\end{lmm}
\begin{proof}
 It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras. Since the unit $\mathbf{1}:Sym(\fg \otimes \Omega(U)[1]) \to B(U)$ is induced, for all $U$, by the factorization structure from the empty set $\emptyset$, we obtain that its support $I_{\mathbf{1}}=\emptyset$. 
 Therefore, formula~\eqref{eq:defineevJ} yields that 
 \[\ev_{f} (\mathbf{1}\otimes X) = \ev_{\emptyset}(\tilde{\mathbf{1}}\otimes X) 
 = \mathbf{f}(X)\] which proves the commutativity.
\end{proof}
